General Relativistic Ray Tracing for Neutrinos

### 2016-09-01 paper.tex
Remove some todos and fix notation

\begin{abstract}
  We present a ray tracing algorithm for computing neutrino distributions in
  general numerical spacetimes with hydrodynamical sources.
  The formulation is fully coordinate invariant and accurately describes
  radiation in regimes spanning optically thick to optically thin.
  We test the new code, highlight its strengths and weaknesses, and
  apply it to estimate power
  liberated by neutrino-antineutrino annihilation in the funnel of a
  post-merger accretion disk.
\end{abstract}

@@

\section{Ray tracing formalism}

@@

Neutrino radiation obeys the relativistic Boltzmann equation
\todo{integral isn't explicitly covariant}
\todo{correct this to differentiate in phase space}
\begin{equation}
  \label{eqn:boltzmann}
  p^\beta \nabla_\beta f = \mathscr{E} - \mathscr{K} f
  + \mathscr{K}_s \oint d\ell' \phi(\ell_\alpha,\ell_\beta') f,
\end{equation}
where $\nabla_\beta$ denotes a covariant derivative. We have introduced
$\mathscr{E}$, the invariant emissivity,
$\mathscr{K}\equiv\mathscr{K}_a+\mathscr{K}_s$, the invariant total opacity
comprised of absorption and scattering opacities, and
$\phi(\ell_\alpha,\ell_\beta')$, the elastic scattering kernel, representing the
likelihood of scattering from the direction $\ell_\beta'$ to the direction
$\ell_\alpha$, subject to the normalization
\todo{confirm this}
\begin{equation}
  \oint d\ell' \phi(\ell_\alpha,\ell_\beta') = 1.
  \nonumber
\end{equation}

>>>>

\begin{abstract}
  We present a ray tracing algorithm for computing neutrino distributions in
  general numerical spacetimes with hydrodynamical sources.
  The formulation is fully coordinate invariant and accurately describes
  radiation in regimes spanning optically thick to optically thin.
  We test the new code, highlight its strengths and weaknesses, and
  apply it to estimate power
  liberated by neutrino-antineutrino annihilation near the hypermassive neutron
  star formed by a merger.
\end{abstract}

@@

\section{Ray tracing formulation}

@@

Neutrino radiation obeys the relativistic Boltzmann equation
\begin{equation}
  \label{eqn:boltzmann}
  \frac{d}{d\lambda}f = \mathscr{E} - \mathscr{K} f
  + \mathscr{K}_s \oint d\Omega' \phi(\ell_\alpha,\ell_\beta') f,
\end{equation}
where $\frac{d}{d\lambda}$ denotes a derivative with respect to the affine
parameter defining the neutrino momentum,
and $d\Omega'$ is the element of area in momentum space, with $\ell_\alpha$
ranging over the sphere.
We have introduced
$\mathscr{E}$, the invariant emissivity,
$\mathscr{K}\equiv\mathscr{K}_a+\mathscr{K}_s$, the invariant total opacity
comprised of absorption and scattering opacities, and
$\phi(\ell_\alpha,\ell_\beta')$, the elastic scattering kernel, representing the
likelihood of scattering from the direction $\ell_\beta'$ to the direction
$\ell_\alpha$, subject to the normalization
\todo{confirm this}
\begin{equation}
  \oint d\ell' \phi(\ell_\alpha,\ell_\beta') = 1.
  \nonumber
\end{equation}
